Compare pseqs

### 2019-06-04 comparepseqs.Rmd
Ready for rmd

@@

```{r plot alpha-beta}
names(rds)
if (!exists("subset.run")) {
    plotlist <- list()

@@

    g <- arrangeGrob(grobs = plotlist, ncol=2)
    ggsave(file="cache/plotlist.png", g, height=6*length(plotlist)/1.5, width=10*2)

} else {
    message("Skipping graphics")
}
```

```{r debug, eval = FALSE}
alphalist <- c()
for (key in names(rds)) {
    alphalist <- c(alphalist,
              ret[[key]]$alphadiversity$min %>% pull(estimate),
              ret[[key]]$alphadiversity$full %>% pull(estimate))
}

summary(alphalist)
```

```{r alpha size, eval = FALSE}
pseq <- import_filter_data(rds[["gtdb"]])

dset <- meta.merge.alphadiversity(pseq) %>%
    mutate(diversities_shannon = scale(diversities_shannon))

dset %>%
    select(MAP, diversities_shannon) %>%
    gather(key, value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       min = min(as.numeric(value), na.rm = TRUE),
                       max = max(as.numeric(value), na.rm = TRUE),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       SD = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    kable()

lm(sprintf(fo.alpha.full, "SYSTM"), data = dset) %>% summary
```

@@

```{r draw alpha distribution scatter plot, eval = FALSE}
scatterplot.df <- lapply(ret, function(x) x$alphadistribution) %>%
    Reduce(function(x, y) merge(x, y, all=TRUE, by="Sample_ID"), .) %>%
    select(-Sample_ID) %>%
    na.omit()

@@

ggsave(file = paste0("cache/ggpairs-alphas.png"),
       plot= galphascatter,
       height=6,
       width=9,
       unit = "in",
       dpi = 300)

```

Full model R2

```{r diff beta debug, eval = FALSE}
betadf <- data.frame()
for (key in names(rds)) {
    moddf.full <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$full) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "full") %>%
        select(term, model, covariates, R2)
    moddf.min <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$min) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "min") %>%
        select(term, model, covariates, R2)
    betadf <- rbind(betadf, moddf.full, moddf.min)
}

@@

```{r debugging adonis, eval = FALSE}
pseq <- import_filter_data(rds[["gtdb"]])

dset <- meta.merge.alphadiversity(pseq) %>%
    mutate(diversities_shannon = scale(diversities_shannon))

bray.dist.matrix <- readRDS(file = paste0("rds-comparepseqs/bray-gtdb.rds"))

dset.sample <- dset %>% sample_n(50)

dset.ids <- dset.sample %>% pull(Sample_ID)

betadiversity <- list(min = calculateadonis(dset = dset.sample,
                                            matrix = bray.dist.matrix[dset.ids, dset.ids],
                                            covariates = covariates.min,
                                            npermutations = 10000),
                      full = calculateadonis(dset = dset.sample,
                                      matrix = bray.dist.matrix[dset.ids, dset.ids],
                                      covariates = covariates.full,
                                      npermutations = 2))

betadiversity$full

betadf <- data.frame()
for (key in names(rds)) {
    moddf.full <- Reduce(function(...) merge(..., all=T), betadiversity$full) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "full") %>%
        select(term, model, covariates, R2)
    moddf.min <- Reduce(function(...) merge(..., all=T), betadiversity$min) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "min") %>%
        select(term, model, covariates, R2)
    betadf <- rbind(betadf, moddf.full, moddf.min)
}
betadf %>% arrange(term) %>% spread(model, R2) %>% kable

```

>>>>

# Calculate alpha and beta diversity

@@

```{r quit subruns}
if (exists("subset.run")) {
    quit()
}
```

# Diversities for BP variables

```{r plot alpha-beta}
plotlist <- list()

@@

g <- arrangeGrob(grobs = plotlist, ncol=2)
ggsave(file="cache/plotlist.png", g, height=8*length(plotlist)/1.5, width=10*2)
```

<img src="cache/plotlist.png"/>

@@

```{r draw alpha distribution scatter plot}
scatterplot.df <- lapply(ret, function(x) x$alphadistribution) %>%
    Reduce(function(x, y) merge(x, y, all=TRUE, by="Sample_ID"), .) %>%
    select(-Sample_ID) %>%
    na.omit()

@@

ggsave(file = paste0("cache/ggpairs-alphas.png"),
       plot= galphascatter,
       height=6,
       width=9,
       unit = "in",
       dpi = 300)
```

<img src="cache/ggpairs-alphas.png"/>

# Beta diversity

Beta diversity R2

```{r beta diversity r2}
betadf <- data.frame()
for (key in names(rds)) {
    moddf.full <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$full) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "full") %>%
        select(term, model, covariates, R2)
    moddf.min <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$min) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "min") %>%
        select(term, model, covariates, R2)
    betadf <- rbind(betadf, moddf.full, moddf.min)
}

@@

Beta diversity p.values

```{r beta diversity pvalue}
betadf <- data.frame()
for (key in names(rds)) {
    moddf.full <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$full) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "full") %>%
        select(term, model, covariates, `Pr(>F)`)
    moddf.min <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$min) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "min") %>%
        select(term, model, covariates, `Pr(>F)`)
    betadf <- rbind(betadf, moddf.full, moddf.min)
}
betadf %>% arrange(term) %>% spread(model, `Pr(>F)`) %>% kable
```
